Discrete Quantum Theories and Computing

### 2018-12-05 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

\begin{table}
\noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical computational
models and their physical realizations\todo{Put the third row in
the middle alignment.}}
\begin{tabularx}{\linewidth}{ccX}
\toprule 
\addlinespace
 & Discrete & Continuum\tabularnewline\addlinespace
\midrule
\addlinespace
\midrule
\addlinespace
Theoretical  Model & Turing machine & BCSS machine\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Physical Realization & Digital Computer & Analog Computer\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
How the models realize? & Reliably & Not Reliably:
\begin{itemize}
\item The quality might be quantized.
\item The precision of an analog computer is low.
\end{itemize}\tabularnewline\addlinespace
\bottomrule
\addlinespace
\end{tabularx}
\end{table}
The situations for classical computation is summarized in Table~\ref{tab:Comparison},
and similar situations could potentially be applied to quantum computation.
\todo{Introduction cleaning up until here. }Similar to classical
analog computers manipulating, say, the position of substance, the
most widely used model of quantum computing, the quantum circuit model,
manipulates the probability amplitudes to do the computation. \todo{Play
with some cloud quantum computers to see if I can find more support
evidence. }Because we are agnostic about whether probability amplitude
is quantized or can really be valued in the continuum of complex numbers,
we tried to develop two different types of models: the quantum theories
and computing over finite fields are discrete models, and the quantum
interval-valued probability measures incorporate the idea of measurement
precision into the quantum theory. To distinguish the modified quantum
theories from the usual ones, the usual ones will be called the ``conventional
quantum theory'' where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
and ``ordinary'' quantum theory.}.
\begin{sidewaystable}
\caption{Comparison among our models}

@@

Values\tabularnewline[\doublerulesep]

@@

\end{tabular} & Unlikely & Yes & Partially & No &  & \tabularnewline\addlinespace

@@

\todo{Beginning of Merge Left}Since conventional probability amplitude
is in the field of complex numbers, and the field structure is essential
to compute the probability from some probability amplitudes, we in
Chapter~\ref{chap:DQT=000026DQC} tried to build discrete quantum
theories and computing by considering them over finite fields.

>>>>

In conventional quantum theory and computation, the probability amplitudes
are modeled by the continuum of complex numbers. This kind of model
doesn't take into account that human doesn't have the ability to distinguish
quantities differing only by an arbitrarily small extent. One possibility
is that the probability amplitudes in quantum theories are quantized.
This leads us to consider quantum theories and computing over finite
fields. Even if the probability amplitudes are actually continuous,
since human has no ability to distinguish the probability computed
by these probability amplitudes, it may be desirable to incorporate
the idea of measurement precision into the quantum theory, and consider
quantum interval-valued probability.
\begin{sidewaystable}
\caption{Comparison among our models, where the upper half of the table lists
their quantum mechanical definitions and properties, and the lower
half of the table lists their computational power.}

@@

Value\tabularnewline[\doublerulesep]

@@

\end{tabular} & Unlikely & Yes & Partially & Unlikely &  & \tabularnewline\addlinespace

@@

\todo{Introduction Cleaned up until here.}

\begin{table}
\noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical computational
models and their physical realizations\todo{Put the third row in
the middle alignment.}}
\begin{tabularx}{\linewidth}{ccX}
\toprule 
\addlinespace
 & Discrete & Continuum\tabularnewline\addlinespace
\midrule
\addlinespace
\midrule
\addlinespace
Theoretical  Model & Turing machine & BCSS machine\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Physical Realization & Digital Computer & Analog Computer\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
How the models realize? & Reliably & Not Reliably:
\begin{itemize}
\item The quality might be quantized.
\item The precision of an analog computer is low.
\end{itemize}\tabularnewline\addlinespace
\bottomrule
\addlinespace
\end{tabularx}
\end{table}
The situations for classical computation is summarized in Table~\ref{tab:Comparison},
and similar situations could potentially be applied to quantum computation.
\todo{Introduction cleaning up until here. }Similar to classical
analog computers manipulating, say, the position of substance, the
most widely used model of quantum computing, the quantum circuit model,
manipulates the probability amplitudes to do the computation. \todo{Play
with some cloud quantum computers to see if I can find more support
evidence. }Because we are agnostic about whether probability amplitude
is quantized or can really be valued in the continuum of complex numbers,
we tried to develop two different types of models: the quantum theories
and computing over finite fields are discrete models, and the quantum
interval-valued probability measures incorporate the idea of measurement
precision into the quantum theory. To distinguish the modified quantum
theories from the usual ones, the usual ones will be called the ``conventional
quantum theory'' where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
and ``ordinary'' quantum theory.}.

\todo{Beginning of Merge Left}Since conventional probability amplitude
is in the field of complex numbers, and the field structure is essential
to compute the probability from some probability amplitudes, we in
Chapter~\ref{chap:DQT=000026DQC} tried to build discrete quantum
theories and computing by considering them over finite fields.
